\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeAchievementsHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Hirnaymay Bhaskar} \\ \vspace{1pt}
    \small +91-7017007660 $|$ \href{mailto:sony.vaio.1404@gmail.com}{\underline{sony.vaio.1404@gmail.com}} $|$ 
    \href{https://linkedin.com/in/hirnaymay}{\underline{linkedin.com/in/hirnaymay/}} $|$
    \href{https://github.com/octopols}{\underline{github.com/octopols}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. A. P. J. Abdul Kalam Technical University}{Lucknow, IN}
      {Bachelor of Technology in Computer Science and Engineering}{Apr 2020 -- Jul 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google Summer of Code 2023 Student}{May 2024 -- Oct 2024}
      {MuseScore}{London, UK(Remote)}
      \resumeItemListStart
        \resumeItem{Transferred the entire MuseScore popup system to a different module, establishing interfaces to minimize coupling. Implemented a popup for editing text in the music sheet with keyboard navigation and additional features.}
        \resumeItem{Orchestrated cross-functional collaboration with design and development teams to flawlessly integrate the popup system}
        \resumeItem{Quickly resolved crucial community-raised issues and also ensured project integrity.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Google Developers Student Clubs, Core Team Member}{Jan 2022 -- Present}
      {Ajay Kumar Garg Engineering College}{Ghaziabad(NCR), UP, India}
      \resumeItemListStart
        \resumeItem{ Orchestrated and facilitated 6 industry-leading workshops, attracting 150+ attendees; collaborated with cross-functional teams to ensure seamless execution and received 98\% positive feedback scores for content and organization.}
        \resumeItem{Played a pivotal role in the event's success by orchestrating compelling visual aids and promotional materials, ultimately driving increased engagement and attendance.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{\href{https://github.com/octopols/coloc_mobile}{\underline{Coloc}}} $|$ \emph{Flutter, Dart, Firebase}}{Jan 2024}
          \resumeItemListStart
            \resumeItem{An android application showcasing adept utilization of Dart, Flutter, and Firebase. Coloc streamlines the roommate-finding process for college students, integrating swipe-based matching and secure messaging functionalities for seamless roommate connections.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://github.com/musescore/MuseScore/pull/18436}{\underline{Text Style Popup}}} $|$ \emph{C/C++, Qt, QML, Cmake, MSVC}}{May 2023}
          \resumeItemListStart
            \resumeItem{Designed and created a crucial pop-up system for text editing in Musescore using C++, Qt, and QML, allowing
            users to access font properties, color, size, spacing, etc directly.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/octopols/Multiple-Overlapping-Object-Detection}{\underline{Multiple Overlapping Object Detection}}} $|$ \emph{HTML, CSS, JavaScript, TensorFlow}}{May 2023}
          \resumeItemListStart
            \resumeItem{Developed a project demonstrating expertise in utilizing pre-trained models in TensorFlow.js for performing multiple object detection in images with high accuracy.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/octopols/wallionary}{\underline{Wallionary}}} $|$ \emph{Kotlin, Android Studio, Firebase, Glide 4}}{Nov 2022}
          \resumeItemListStart
            \resumeItem{Crafted and launched Wallionary, an Android application created to help users improve their vocabulary by updating their wallpaper with new words on a daily basis.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeSubheading{Google Summer of Code 2023}{Jun 2023}{Selected as one of 967 students out of 43,765 applicants from 65 countries.}{\href{https://summerofcode.withgoogle.com/programs/2023/projects}{\underline{Accepted Candidates List}}}
      \resumeSubheading{Google Cloud Practitioner Program (Cloud Engineer Learning Path)}{Dec 2022}{Finished the Cloud Engineer Learning Path.}{\href{https://www.cloudskillsboost.google/public_profiles/19b211dc-6aa0-4b6f-a1bb-58c00b38c43e}{\underline{Cloud Skill Boost Profile}}}
      \resumeSubheading{CodeChef November Challenge 2021 Division 3 (Rated)}{Nov 2021}{Global Rank 87 out of 16037 people}{\href{https://www.codechef.com/rankings/NOV21C}{\underline{Rank List}}}
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, JavaScript, Kotlin, Dart, HTML/CSS} \\
     \textbf{Frameworks}{: Android SDK, Flutter, MediaPipe, Android Jetpack} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, Qt Creator, Android Studio, Firebase} \\
     \textbf{Libraries}{: QtQuick, QtCore}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}